### 2019-12-15 thesis/txt/6-discussion.tex
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text

Extracting the average number of lines present in the training examples seems to give the best balance of precision and recall for CTS\@.

@@

\subsection{Keyword Search (KWS)}
\paragraph{Configuration and Input}
KWS has a higher recall than both other techniques for multiple structural categories present in the training and test examples.\@.
This makes KWS a good technique if there is little prior knowledge on how the desired BLI is represented in the build log to be analyzed.
For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.

@@

>>>>

Extracting the average number of lines present in the training examples gives the best retrieval results for CTS, according to the F$_{1}$-score.

@@

\subsection{Keyword Search (KWS)}
\paragraph{Configuration and Input}
KWS has a higher recall than both other techniques for multiple structural categories present in the training and test examples.\@.
This makes KWS a good technique if there is little prior knowledge on how the targeted log chunk is represented in the build log to be analyzed.
For the example of extracting the reason the build failed, KWS is best suited if a build can fail in various steps logged by different tools and no pre-categorization of where the build failed is available.

@@

\paragraph{Example of Using the Recommendation Scheme}
To illustrate how one would use our decision tree to find a suitable chunk retrieval technique we follow with describing two concrete examples: a researcher investigating why CI builds fail and a software team wanting to monitor their build performance.

In our first example, a researcher studies whether there test failures in CI are caused by a small or by a large group of test cases.
They gather CI build logs from various projects, which are their only available data source.
The task of the researcher is to extract the name of the failing test case from each build log.
When they use our recommendation scheme to select a chunk retrieval technique, they first have to estimate how uniform the representation of the failing test case is in the investigated build logs.
As the researcher is covering a wide range of build tools and development languages, the log chunks they target are in various, not predictable structural representations.
The next question is whether they value precision over recall.
As they have to manually inspect the results of both CTS and KWS, they choose recall over precision to avoid having to inspect the whole log in case the relevant information chunk was not retrieved.
Therefore, our decision tree recommends them to use KWS\@.

In case the researchers want to avoid manually inspecting the retrieval results, they have to first separate the CI build logs according to the test tool responsible for logging the test results.
Then the targeted log chunks are from one structural category and they can use PBE, trained with examples from each tes tool separately.

In our second example, a software development team wants to monitor the performance of the phases within their CI build.
They are using Travis CI, which measures the duration of build phases and documents them within the build log.
As all log statements that report timing measurements are formatted the same way, the targeted log chunks are from one structural category.
Therefore the development team can use PBE to retrieve the duration of a build phase as well as its name.

### 2019-12-15 thesis/txt2/4-tool.tex
describe more examples, add example application of reccomendation sceme, abstract, overview pictures, f1 score in text

\chapter{Tool Implementation}
\label{sec:implementation}
To evaluate PBE, CTS and KWS on \emph{LogChunks} we implemented them and a unifying interface to retrieve chunks from build logs.

@@

The unified interface is implemented in Ruby and gives access to all the CTRs we implemented.
This section describes how to use it to retrieve chunks for a build log or evaluate a CRT.
% As we implemented the information retrieval techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interface. Our unified interface then in turn calls the various different IE techniques over the command line.

To retrieve chunks from a build log use the option \texttt{-a analyze} with these options:
\begin{itemize}
    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. For pbe, ir and random analysis only. See Section \ref{sec:example-set} for the definition of an example set.
    \item \texttt{-p} \textbf{Build Log Path} The path to the file to be analyzed.
    \item \texttt{-k} \textbf{Keywords} The keywords to search for, only for keyword analysis.
\end{itemize}

To evaluate a CTR use the option \texttt{-a evaluate} with these options:
\begin{itemize}
    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. See Section \ref{sec:example-set} for the definition of an example set.
    \item \texttt{-s} \textbf{Selection Technique} \texttt{chronological, random or manual} How the order of the examples should be selected during learning.
    Manual selects the examples according to the sequence defined in the example set file.
    \item \texttt{-l} \textbf{Learning Step Count} How many learning steps should be evaluated, the maximum number of examples to learn with.
    The referenced example set must define at least \emph{Learning Step Count + Test Count} examples.
    \item \texttt{-t} \textbf{Test Count} On how many following examples the learned technique should be tested.
    Currently only \texttt{1} is supported.
\end{itemize}

@@

% We provide two different modes: \emph{analysis} and \emph{evaluation}.
% The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting retrieval on the console output. The \emph{evaluation} takes an

% unification tool, reference CLI somehow nicely?,

% ruby tool, unifies different syntax command line interfaces of the other tools, easy to switch between different techniques (NOT TOO LONG)

%\section{Overall Implementation Remarks}
% There are multiple implementation specialities that span over all languages, frameworks and implemented techniques.
% The following section discusses preprocessing and escaping of the parsed build log files / example sets, as well as\textellipsis \todo{more?}

% \subsection*{Preprocessing Log Text}
% \label{sec:impl-preprocessing}

%\section*{PBE}
% \paragraph{Program Synthesis by Example (PBE)}
% \label{sec:impl-pbe}
% Our implementation of the PBE chunk retrieval in C\# is based on the Microsoft PROSE library~\cite{prose2019webpage}.
% % The first technique we implemented was the PROSE regular expression program synthesis. As it is based on the PROSE library from Microsoft provided in C\# we also chose C\# for our tool. 
% % implementation details :)

% % C\#, based on PROSE Text Extraction DSL, parsing example set files, feeding learning session \& applying learned regex program, can do single string extraction and also sequence extraction \& showing differentiating examples (although not in use)

% \paragraph{Common Text Similarity (CTS)}
% \label{sec:impl-ts}
% We implemented the CTS chunk retrieval using R and the text2vec library.

% % impl details,

% % R, text2vec, tokenized vectors, impl of preprocessing?

% % don't repeat from IE models section!

% \paragraph{Keyword Search (KWs)}
% \label{sec:impl-skws}
% impl details,

% R, simple!

>>>>

\chapter{Tool Implementation}
\label{sec:implementation}
To evaluate PBE, CTS and KWS on \emph{LogChunks} we implemented them and a unifying interface to retrieve information chunks from build logs.

@@

The unified interface is implemented in Ruby and gives access to all the chunk retrieval techniques we implemented.
This section describes how to use it to retrieve chunks for a build log or evaluate a chunk retrieval technique.

To retrieve an chunk from a build log use the option \texttt{-a analyze} with these options:
\begin{itemize}
    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. For pbe, ir and random analysis only. See Section~\ref{sec:example-set} for the definition of an example set.
    \item \texttt{-p} \textbf{Build Log Path} The path to the file to be analyzed.
    \item \texttt{-k} \textbf{Keywords} The keywords to search for, only for keyword analysis.
\end{itemize}

To evaluate a CTR use the option \texttt{-a evaluate} with these options:
\begin{itemize}
    \item \texttt{-t} \textbf{Technique} \texttt{pbe, ir, keyword or random}. Specify which technique to use for extraction.
    \item \texttt{-e} \textbf{Examples Set} The example set used to configure the technique. See Section~\ref{sec:example-set} for the definition of an example set.
    \item \texttt{-s} \textbf{Selection Technique} \texttt{chronological, random or manual} How the order of the examples should be selected during learning.
    Manual selects the examples according to the sequence defined in the example set file.
    \item \texttt{-l} \textbf{Learning Step Count} How many learning steps should be evaluated, the maximum number of examples to learn with.
    The referenced example set must define at least \emph{Learning Step Count + Test Count} examples.
    \item \texttt{-t} \textbf{Test Count} On how many following examples the learned technique should be tested.
    Currently only \texttt{1} is supported.
\end{itemize}

@@
